---
title: "Introduction to ClusterCirc"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to ClusterCirc}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ClusterCirc)
```

ClusterCirc is a clustering method designed for data with circular
structure. It can be used to find item clusters with optimal circumplex
spacing as an alternative to other clustering techniques like
conventional cluster analysis.

ClusterCirc can be applied to raw data or on item loadings on two
orthogonal factors or components from principal component analysis,
exploratory or confirmatory factor analysis. If ClusterCirc is used on
raw data, principal component analysis is performed before ClusterCirc
to yield loadings on two unrotated components.

The ClusterCirc algorithm uses item loadings and translates them into
angles in a circular arrangement by trigonometric conversion.
ClusterCirc then sorts items into clusters that yield optimal circumplex
spacing.

Optimal circumplex spacing for item clusters is given if clusters are
evenly distributed across the circle (equal spacing between clusters)
and if items are clustered closely around their cluster centroid
(minimal within-cluster spacing). Spacing coefficients are computed to
assess circumplex spacing of items, clusters, and the overall data.
Range of all ClusterCirc coefficients: 0-1 (0 = perfect circumplex
spacing).

**There are two functions for users:**

1.  **cc_data:** Main function. Sorts items of your dataset into
    clusters with optimal circumplex spacing. Spacing coefficients are
    computed for the suggested clustering. Depends on function cc_raw,
    which is included in the ClusterCirc package and automatically
    performed when cc_data is called.

2.  **cc_simu:** Can be used to assess circumplex fit of the dataset.
    The function uses the specifications of the data and creates 500
    samples from a population with perfect circumplex spacing of
    clusters. Results for the dataset (spacing coefficients from
    cc_data) are compared to results from cc_simu to evaluate
    circumplexity in the data. cc_simu can only be used after performing
    cc_data.

See function documentation for description of parameters (?cc_data, ?cc_simu).

**Using ClusterCirc functions on exemplary (simulated) data:**

Perfect circumplex clusters with n = 100 subjects, p = 3 clusters, m =
18 variables.

**1. cc_data:**

```{r}
cc_data(file = data_ex, type = "scores", p = 3, m = 18, q = 10)
```

**2. cc_simu:**

```{r}
cc_simu(100)
```
