---
title: "Introduction to ClusterCirc"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to ClusterCirc}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ClusterCirc)
```

ClusterCirc is a clustering method designed for data with circular
structure. It can be used to find item clusters with optimal circumplex
spacing as an alternative to other clustering techniques like
conventional cluster analysis.

ClusterCirc is based on item angles. Input data can be item angles directly,
raw data, or item  loadings on two orthogonal factors or components from principal component analysis, exploratory or confirmatory factor analysis. If the data file
contains raw data, item angles can be obtained by performing PCA (default) and converting the resulting loadings on two unrotated components into angles or by performing Browne's procedure CIRCUM on the data. 

ClusterCirc then sorts items into clusters that yield optimal circumplex
spacing. Optimal circumplex spacing for item clusters is given if clusters are
evenly distributed across the circle (equal spacing between clusters)
and if items are clustered closely around their cluster centroid
(minimal within-cluster spacing/item heterogeneity). Spacing coefficients 
are computed to assess circumplex spacing of items, clusters, and the overall data.
Range of all ClusterCirc coefficients: 0-1 (0 = perfect circumplex spacing).

**There are three functions for users:**

1.  **cc_data:** Main function. Sorts items of your dataset into
    clusters with optimal circumplex spacing. Spacing coefficients are
    computed for the suggested clustering. Depends on function cc_raw,
    which is included in the ClusterCirc package and is automatically
    performed when cc_data is called.

2.  **cc_simu:** Can be used to assess circumplex fit of the dataset.
    The function uses the specifications of the data and creates samples
    from a population with perfect circumplex spacing of clusters (default
    number of samples = 500). Results for the dataset (spacing coefficients 
    from cc_data) are compared to results from cc_simu to evaluate
    circumplexity of the data. cc_simu can only be used after performing
    cc_data.
    
3.  **cc_fix:** Computes ClusterCirc coefficients for user-defined item clusters
    without performing the ClusterCirc search algorithm to find item clusters.
    ClusterCirc-Fix coefficients for user-defined item clusters can be compared
    to ClusterCirc coefficients for item clusters found by ClusterCirc-Data.

See function documentation for description of parameters:
?cc_data, ?cc_simu, ?cc_fix.

**Using ClusterCirc functions on exemplary (simulated) data:**

Perfect circumplex clusters with n = 300 subjects, p = 3 clusters, m =
18 variables.

**1. cc_data:**

```{r}
cc_data(file = data_ex, n_sample = 300, input = "PCA", p = 3,
        n_var = 18, w_com = TRUE, w, comm, e_def = TRUE, e, q = 10)
```

**2. cc_simu:**

```{r}
cc_simu(samples = 500, alpha = 1, input = "PCA")
```

**3. cc_fix:**

```{r}
cc_fix(file = data_ex, n_sample= 300, input = "PCA", limits = c(6,10,18),
       p = 3, n_var = 18, w_com = TRUE, comm, w, e_def = TRUE, e)
```
